\input{headers/main_header}

\begin{document}

\begin{frame}[plain]
    \titlepage
% \footnote{
%     \tiny{
%         Slides heavily borrowed from previous Fall22 TA:\\
%         Sitao Wang -- sitao.wang@mail.utoronto.ca,
%         Devin Gibson -- devin.gibson@mail.utoronto.ca
%     }
% }

\footnotetext[1]{Heavily Borrowed from previous Fall22 TAs Devin Gibson \& Sitao Wang}
\end{frame}
\begin{frame}{Tutorial sections}
    Total of 8 sections for tutorials, around 60 students in each tutorial section.
    \begin{itemize}
        \item Louis:
        \begin{itemize}
            \item TUT101 W 4PM @\textit{GB303}
            \item TUT105 TH 2PM @\textit{BA1130}
        \end{itemize}
        \item Michail:
        \begin{itemize}
            \item TUT102 W 4PM @\textit{MB128}
            \item TUT106 TH 2PM @\textit{HA403} 
        \end{itemize}
        \item Yvonne:
        \begin{itemize}
            \item TUT103 F 9AM @\textit{BA1200}
            \item TUT107 TH 9AM @\textit{GB244} 
        \end{itemize}
        \item Yi Fan:
        \begin{itemize}
            \item TUT104 F 9AM @\textit{GB119}
            \item TUT108 TH 9AM @\textit{GB248} 
        \end{itemize}
    \end{itemize}
\end{frame}
    

\begin{frame}{Introduction to Tutorials}
    \begin{itemize}
        \item \textit{TA brief self-introduction}
        \item Attendance is not mandatory (Is ANYTHING mandatory?)
        \item Format is 25\% Concept Review, 75\% Problem Solving
        \item Focus on past exam questions of \textbf{increasing} difficulty
        \item Participation is important, this is not a lecture!
    \end{itemize}
\end{frame}

\begin{frame}{Reaching out to TAs}
    \begin{itemize}
        \item Most questions can be asked on Piazza
        \item Email TAs to make appointments if necessary (refer to slide 1 for tutorial TAs)
        \item Usually available for 10 minutes after tutorial
        \item Lab questions should be directed towards lab TAs
        
    \end{itemize}
\end{frame}
\begin{frame}{Expectations}
    \begin{itemize}
        \item What Expectations do you have for us?
        \item Any questions on logistics and format?
    \end{itemize}
\end{frame}

\begin{frame}{Reminders}
    \begin{itemize}
        \item Lab 1 Due Saturday September 14
    \end{itemize}
\end{frame}


% \begin{frame}{C++ basics}
%     C is basically* (almost) a subset of C++. So anything you have previously learned in is also legal in C++...
%     \begin{itemize}
%         \item variable types are fixed \texttt{int bool}
%         \item \texttt{main} is the entry point of the program \texttt{int main() {...}}
%     \end{itemize}

%     Experience with other "popular languages" such as Python is useful
% \end{frame}

% \begin{frame}{Why C++?}
%     \begin{itemize}
%         \item Performance... With good amount of features
%     \end{itemize}
% \end{frame}

% \begin{frame}{Why Not C++?}
%     (Only) 25 \% of developers use C++ (Stack Overflow Survey)
%     \begin{itemize}
%         \item Web Applications
%         \item Easier to get started...
%     \end{itemize}
    
% \end{frame}
\begin{frame}[fragile]{Exercise \#1: There was once an interview question...}

Did you know that you can draw different shapes on the console?

    \begin{itemize}
        \item Task 1: Draw a square of height X
        \item Task 2: Draw a triangle of height Y
        \item examples provided for X=5, Y=5, shown side-by-side, Task 1 and Task 2 are independent.    % Complexity examples
        \begin{lstlisting}
        #####       #
        #####      ##
        #####     ###
        #####    ####
        #####   #####
(shown side by side for space reasons) \end{lstlisting}
    \end{itemize}      


\end{frame}

\begin{frame}{Exercise \#2: How pointers were discovered when swapping numbers???}

    \begin{itemize}
        \item Task A: Given integer variables foo = X, and bar = Y, how can you write a swap procedure that swaps foo and bar, such that bar = Y, foo = X
    
        \item Task B: Task A, but using a function called \texttt{swap()}
    
        \item Task C: Task B, but you cannot use any pointers! Can C++ do it?
        Hint: pass-by-reference
    \end{itemize}      
\end{frame}

\begin{frame}{Exercises from the textbook}
    \href{https://learningcpp.org/chapters/chapter01-basics/exercises}{CLICK ME}
\end{frame}

\end{document}